Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;educator </font>

### 2022-12-23 index.Rmd
mastodon link

Besides research and teaching and consulting and whatnot, I (fortunately) also do some other things, which mostly consist of dance (lindy hop, salsa, bachata), boardgames, and outdoorsy stuff (running, hillwalking).

### Before Edinburgh

@@

<div style="text-align: center; align:center"> 
<IMG SRC="round.jpg"> 
<br>
<br>
<br>
Andres Karjus, research fellow, CUDAN lab, Tallinn University<br>
&nbsp;&nbsp;&nbsp;<a href="mailto:andres.karjus --at-- tlu.ee">email</a>  |  <a href="https://twitter.com/AndresKarjus">twitter</a>
<br>
</div>

>>>>

Besides research and teaching and consulting and whatnot, I (fortunately) also do some other things, which mostly consist of dance (lindy hop, salsa, bachata), boardgames, and outdoorsy stuff (running, hiking).

### Before the PhD in Edinburgh

@@

<div style="text-align: center; align:center"> 
<IMG SRC="round.jpg"> 
<br>
<br>
<br>
**Andres Karjus** <br> 
Research fellow, CUDAN Open Lab, Tallinn University <br>

Email: andres.karjus --at-- tlu.ee <br>
Twitter: <a href="https://twitter.com/AndresKarjus">https://twitter.com/AndresKarjus</a> <br>
Mastodon: <a href=https://mastodon.social/@andreskarjus>https://mastodon.social/@AndresKarjus</a>
<br>
</div>
